\pisodm: Building Service-Oriented Applications in the Presence of Non-Functional Requirements

### 2015-04-23 JournalToSubmit2015/submitted/main.tex
submitted to the chinese journal

\author{Khalid Belhajjame$^1$, Valeria~de~Castro$^2$, Umberto~Souza~da~Costa$^3$, Javier~A.~Espinosa-Oviedo$^4$, Martin~A.~Musicante$^{3,*}$, Pl\'acido~A.~Souza~Neto$^5$, Genoveva~Vargas-Solar$^6$, \\ Jos\'e-Luis~Zechinelli-Martini$^4$}

\footnotetext{$^*$.Corresponding author.}
\footnotetext{$^1$.Universit\'e de Paris - Dauphine -- Paris, France.
\textsl{kbelhajj@googlemail.com}.
}
\footnotetext{$^2$.Universidad Rey Juan Carlos -- M\'{o}stoles, Spain.
\textsl{valeria.decastro@urjc.es}.
}
\footnotetext{$^3$.Universidade Federal do Rio Grande do Norte -- Natal, Brazil.
\textsl{\{umberto,mam\}@dimap.ufrn.br}.
}
\footnotetext{$^4$.Universidad de las Am\'ericas-Puebla, LAFMIA -- Cholula, Mexico.
\textsl{javiera.espinosa@gmail.com}, \textsl{joseluis.zechinelli@udlap.mx}.
}
\footnotetext{$^5$.Instituto Federal de Educa\c{c}\~{a}o, Ci\^{e}ncia e Tecnologia do Rio Grande do Norte -- Natal, Brazil.
\textsl{placido.neto@ifrn.edu.br}.
}
\footnotetext{$^6$.CNRS, LIG-LAFMIA, Saint Martin d'H\`eres, France.
\textsl{genoveva.vargas@imag.fr}.
}

>>>>

%\author{Khalid Belhajjame$^1$, Valeria~de~Castro$^2$, Umberto~Souza~da~Costa$^3$, Javier~A.~Espinosa-Oviedo$^4$, Martin~A.~Musicante$^{3,*}$, Pl\'acido~A.~Souza~Neto$^5$, Genoveva~Vargas-Solar$^6$, \\ Jos\'e-Luis~Zechinelli-Martini$^4$}

%\footnotetext{$^*$.Corresponding author.}
%\footnotetext{$^1$.Universit\'e de Paris - Dauphine -- Paris, France.
%\textsl{kbelhajj@googlemail.com}.
%}
%\footnotetext{$^2$.Universidad Rey Juan Carlos -- M\'{o}stoles, Spain.
%\textsl{valeria.decastro@urjc.es}.
%}
%\footnotetext{$^3$.Universidade Federal do Rio Grande do Norte -- Natal, Brazil.
%\textsl{\{umberto,mam\}@dimap.ufrn.br}.
%}
%\footnotetext{$^4$.Universidad de las Am\'ericas-Puebla, LAFMIA -- Cholula, Mexico.
%\textsl{javiera.espinosa@gmail.com}, \textsl{joseluis.zechinelli@udlap.mx}.
%}
%\footnotetext{$^5$.Instituto Federal de Educa\c{c}\~{a}o, Ci\^{e}ncia e Tecnologia do Rio Grande do Norte -- Natal, Brazil.
%\textsl{placido.neto@ifrn.edu.br}.
%}
%\footnotetext{$^6$.CNRS, LIG-LAFMIA, Saint Martin d'H\`eres, France.
%\textsl{genoveva.vargas@imag.fr}.
%}
